---
title: "QuARTS-2_Results Preview"
output: pdf_document
date: "2024-12-02"
author: "by Abbey S. Nydam"
---

```{r setup, include=FALSE}
# knitr::opts_chunk$set(echo = TRUE) # for debugging so shows errors
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.width = 10, fig.height = 5)
# knitr::opts_chunk$set(echo = TRUE, fig.width = 10, fig.height = 5)

library(shiny)
library(bslib)
library(reshape2)
library(ggplot2)
library(dplyr)
library(forcats)
library(hrbrthemes)
library(viridis)
library(tidyr)
library(readxl)

# install.packages("devtools")
library("ggpubr")


# # Clear memory
# rm(list = ls()) # clears variables in the environment
# gc() #clears unused mem
# rm() #removes all variables
# Ctrl+Shift+F10 #removes all variables and packages loaded


# Next STEPS!!
# make RMT plot, make Onset Cx the variable (in collate?)
# other?
# get new data from Lianre???

```

## QuARTS 2 Data - SICI and SICF

## Before running this script, ensure you have run "collate_mem" to produce the raw excel csv file

using script "collate_MEM_Q2_TMS_v6...
or using function:
result <- collate_all(Q2_TMS_collated)

### Data Preview


```{r data_preview, echo=FALSE}

# re-extract data if need be... to update the latest raw data file (*note as for now, this script is using a diff filename for debugging)
#
list_subj_nums <- c('201','203','204','205') #no 202?
source_dir <- "C:/Users/AbrahaoLab/Sync/Abrahao Lab/Abbey Analysis/Analysis/QuARTS2_TMS/1.SourceData"

# result <- collate_all(list_subj_nums,source_dir)


# Import The Raw Data File

df0 <- readfile <- read.csv("2.RawData/QuARTS2_Raw_TMS_extracted_n=4.csv", header=TRUE, sep=";", na.strings = c("", "NA", "NaN"), stringsAsFactors = TRUE)

# ---------------------------
# Tidy Up
# ---------------------------

# remove unneeded variables

df1 <- df0 %>% 
  select(-c('X','Group', 'Site','Date', 'TotalPulses', 'Diff_percent')) %>% 
  mutate(VisitDay = gsub("AY", "", as.character(VisitDay))) %>% # sub 1 had diff filenames, so renaming for consistency
  mutate(VisitDay = gsub("WK3", "WK03", as.character(VisitDay))) %>% # sub 1 had diff filenames, so renaming for consistency
  mutate(VisitDay = gsub("WK5", "WK05", as.character(VisitDay))) %>% # sub 1 had diff filenames, so renaming for consistency
  mutate(VisitDay = gsub("WK7", "WK07", as.character(VisitDay))) %>% # sub 1 had diff filenames, so renaming for consistency
  mutate(VisitDay = gsub("WK9", "WK09", as.character(VisitDay))) %>% # sub 1 had diff filenames, so renaming for consistency
  mutate(ISI_ms = gsub(",", ".", as.character(ISI_ms))) %>%
  mutate(Value_MSO = as.numeric(gsub(",", ".", as.character(Value_MSO)))) %>% # set as numeric with decimals
  mutate_if(is.character, as.factor)  %>% # set as factor
  arrange(ID, VisitDay)

df1$ID <- as.factor(df1$ID) # set as factor

# Create a new variable Time

df1$Time <- sub(".*(AM|PM)$", "\\1", df1$VisitDay)

# Remove "LCX ", "RCX ", "AM", and "PM" to simpify Visit Day

df1$VisitDay <- as.character(df1$VisitDay)  # Convert factor to character
df1$VisitDay <- gsub("LCX |RCX |AM|PM", "", df1$VisitDay)
df1$VisitDay <- as.factor(df1$VisitDay) # Convert back to factor (if needed)
unique(df1$VisitDay) # Check unique values to confirm changes


# Create new_onset_cx variable based on Onset_Cx

excel_path <- "2.RawData/QuARTS-2 Demographic Data v1.0.xlsx"  # Update with actual file path
sheet_name <- "Sheet1"

# Read the Onset_Cx data from the "Demographics" sheet
demographics_data <- read_excel(excel_path, sheet = sheet_name) %>%
  select(ID, Onset_cx)  # Ensure the Excel sheet has these columns
#make new variable in df

# Merge with the main dataframe and fill Onset_Cx for all rows per ID
df1 <- df1 %>%
  left_join(demographics_data, by = "ID") %>%
  mutate(Onset_Cx = ifelse(Onset_cx == L_or_R_cx, "Onset_side", "Non_onset_side"))
  

is_grouped_df(df1) # to check if grouped # ungroup()
# Print the updated data frame
print(df1)

# select 1 subject??

# df1 <- df1 %>% filter(ID %in% c('1','3','4','5','6','7','8'))

# Get variables of interest for TSICI data...

df <- df1 %>% 
  filter(Test %in% c('tSICIp')) %>% # Onset_Cx_side
  # filter(!Test %in% c('NA')) %>% # odd error?? check collate MEM
  select(c('ID','L_or_R_cx', 'Onset_Cx','VisitDay', 'Time','ISI_ms', 'Value_MSO')) %>%      # '
  filter(ISI_ms %in% c(2.5, 3)) %>% #  rationale??
  arrange(ID, L_or_R_cx, Onset_Cx, VisitDay, Time)

# Preview data to screen

head(df,10)

      
```

## Check for Odd Values
```{r checking, echo=FALSE}

# ----------------------------------------
# Check some things...
# ----------------------------------------


max(df_avg$Value_MSO)
min(df_avg$Value_MSO)
unique(df1$VisitDay)
unique(df1$ISI_ms)
unique(df1$Onset_Cx)
unique(df1$Test)
unique(df1$CondStim)
unique(df1$ID)

# Create a summary table
summary_table <- data.frame(
  Statistic = c("Mean Value_MSO", "Max Value_MSO", "Min Value_MSO", 
                "Unique VisitDay", "Unique ISI_ms", "Unique Onset_Cx", 
                "Unique Test", "Unique CondStim", "Unique ID"),
  Value = c(mean(df_avg$Value_MSO, na.rm = TRUE), 
            max(df_avg$Value_MSO, na.rm = TRUE), 
            min(df_avg$Value_MSO, na.rm = TRUE), 
            paste(unique(df1$VisitDay), collapse = ", "), 
            paste(unique(df1$ISI_ms), collapse = ", "), 
            paste(unique(df1$Onset_Cx), collapse = ", "), 
            paste(unique(df1$Test), collapse = ", "), 
            paste(unique(df1$CondStim), collapse = ", "), 
            paste(unique(df1$ID), collapse = ", "))
)

# Print summary table
print(summary_table)

```

## screening Plot - all data
```{r screening, echo=FALSE}

# Check MSO values are reasonable

# Create the plot
p <- ggplot(df1, aes(x = Value_MSO, fill = as.factor(VisitDay), color = ID)) +
  geom_histogram(binwidth = 5, alpha = 0.6, position = "identity") + 
  facet_grid(. ~ ISI_ms) +  # Facet by ISI_ms (Test Level)
  scale_fill_viridis_c(option = "C", name = "Visit Day") +  # Continuous shading
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "right",
    strip.text = element_text(size = 14, face = "bold")
  ) +
  labs(
    title = "Distribution of Value_MSO Across Test Levels",
    x = "Value_MSO",
    y = "Count",
    color = "ID"
  )


# Create a violin plot with tiny scatter behind it - working but not optimized
scatter <- ggplot(df_filtered, aes(x = as.factor(ISI_ms), y = Value_MSO, color = as.factor(ID))) +
  # Violin plot
  geom_violin(trim = TRUE, alpha = 0.8, size = 0.8) +
  # Scatter plot behind violin plot with some transparency
  geom_jitter(aes(color = as.factor(ID)), width = 0.1, height = 0, line_width = 1, alpha = 0.4) +
  # Adjust color scale
  scale_color_manual(values = rainbow(length(unique(df_filtered$ID)))) + 
  # Rescale y-axis (RMT %)
  scale_y_discrete(
    breaks = seq(60, 120, by = 2),  # Show only ticks at 60, 70, 80, 90, 100
    labels = seq(60, 120, by = 2)   # Ensure ticks are displayed as integers
  ) +
  # Labels and title
  labs(
    title = "Violin Plot of Value_MSO by ID with Tiny Scatter",
    x = "ISI",
    y = "RMT %",
    color = "ID"
  ) +
  theme_minimal() + # Clean theme
  theme(legend.position = "right") # Position the legend

scatter

# # Example Data
# df_summary <- data.frame(
#   YYYY = c(2023, 2023, 2024, 2024),
#   Visits = c(15, 20, 25, 30)
# )



```

## SICI Plot - all data
```{r plot_SICI, echo=FALSE}

# ----------------------------------------
# Averages Baseline 
# ----------------------------------------

# new attempt...
# Compute the average Value_MSO for BSL D1 and BSL D2, keeping other variables
df_avg <- df1 %>%
  mutate(VisitDay = ifelse(grepl("BSL D1|BSL D2", VisitDay), "BSL_Ave", as.character(VisitDay))) %>% # VisitGroup
  group_by(ID, Onset_Cx, Time, ISI_ms, VisitDay) %>% #L_or_R_cx
  summarise(Value_MSO = mean(Value_MSO, na.rm = TRUE), .groups = "drop") %>% #Average_Value_MSO
  arrange(ID, Onset_Cx, Time, ISI_ms)

# Print the result
print(df_avg)

# Display the final dataframe
print(df_with_avg)

# kinda working - averages over Days, not AM/PM


# ----------------------------------------
# MAIN PLOT of SICI!!!
# .............Use the PMs for TXs...
# ----------------------------------------

# plot plot_data <- L_or_R_cx
# NEED TO REDO for ONSET COrtex
plot <- df_avg %>% #plot_data %>% was df # was working df1
  filter(Time %in% c('PM')) %>% # Onset_Cx
  # filter(ISI_ms %in% c(2.5)) %>%
  select(c('ID','Onset_Cx', 'VisitDay', 'Value_MSO', 'ISI_ms')) %>%    # Onset_Cx  or L_or_R_cx
  # average over 2.5 and 3 or just 2.5
  filter(ISI_ms %in% c(2.5)) %>%
  group_by(ISI_ms, ID, VisitDay, Onset_Cx) %>% #Onset_Cx
  summarise(Ave_RMT_Change = mean(Value_MSO),
            Ave_SD = sd(Value_MSO, na.rm = TRUE)
            ) %>%
  # summarise(Ave_Diff = ave(Diff_percent)) %>% 
  # mutate(name = fct_relevel(Visit_day, 
  #           "north", "north-east", "east", 
  #           "south-east", "south", "south-west", 
  #           "west", "north-west")) 
  ggplot(aes(x=VisitDay,y=Ave_RMT_Change, 
             ymin = Ave_RMT_Change-Ave_SD, ymax = Ave_RMT_Change+Ave_SD, 
             group_by = Onset_Cx, color = Onset_Cx)) +
  # add a line to mark the baseline
  # geom_rect(aes(xmin = 0.3, xmax = 2.6, ymin = -Inf, ymax = Inf), 
            # fill = "lightgrey", alpha = 0.06, color = NA) + 
  geom_line(aes(y = Ave_RMT_Change, group = Onset_Cx, color = Onset_Cx)) +
  geom_point() +
  # annotate("text", x = 1.5, y = 140, label = "Baseline", size = 5) +  # Add text at (1.5, 140)
    # Add text annotation above the legend
  annotate("text", 
           x = 2.5, y = max(df_avg$Value_MSO) + 5,  # Positioning text above legend
           label = "Characteristics\n201 --> L onset, LL\n202 --> NA R onset, Bulbar\n203 --> R onset, UL\n204 --> L onset, UL\n205 --> L onset, UL", 
           hjust = 0, vjust = 1, 
           size = 5, color = "black")  +
  xlab("Day") + ylab("Inhibition (%)") + #Change in Machine Intensity
  # scale_x_discrete(labels=c("B1", "B2","d1", "d5", "w3", "w5", "w7","w9", "w12","w16","w20","w24")) +
  # scale_y_continuous(breaks=seq(-20,40,by=10)) +
  scale_y_continuous(breaks=seq(80,140,by=10)) +
  facet_wrap( ~ ID) +
  theme_grey() + # theme_classic2
  theme(axis.title=element_text(size=14),
        axis.text=element_text(size=12),
        strip.text=element_text(size=14),
        axis.text.x = element_text(angle = 45, hjust = 1))

plot <- plot + geom_errorbar(width = 0.2)


# STYLE OPTIONS
# plot + theme(legend.position = c(0.9, 0.3))
# 
# plot + geom_rect(aes(xmin = 2, xmax = 3, ymin = -Inf, ymax = Inf), 
#             fill = "lightgrey", alpha = 0.2) +  # Highlight area between x = 2 and x = 3
#   theme_minimal()


# Create the OUTPUT directory if it doesn't exist
if (!dir.exists("4.Output")) {
  dir.create("4.Output")
}


# Save as PDF (Portrait)
ggsave("4.Output/Q2_tSICI_2.5_ave.pdf", plot = plot, width = 11, height = 8, units = "in")

# Save as PNG
ggsave("4.Output/Q2_tSICI_2.5_ave.png", plot = plot, width = 10, height = 8, dpi = 300)



# ----------------------------------------
# Run MCD test....
# ----------------------------------------

# Load necessary libraries
library(dplyr)
library(tidyr)

# Step 1: Calculate standard deviation of MSO values for each individual (ID) and VisitDay
# We assume each subject has repeated measures (10 visits in total), and we calculate the SD for these measures.
sd_by_individual <- df1 %>%
  group_by(ID, VisitDay) %>%
  summarise(
    SD = sd(Value_MSO, na.rm = TRUE),
    n = n(),
    .groups = 'drop'
  )

# Step 2: Calculate SEM for each individual (assuming r = 1 for simplicity)
# Since you don't have reliability values (like ICC), SEM is simply SD / sqrt(n)
sd_by_individual <- sd_by_individual %>%
  mutate(
    SEM = SD / sqrt(n)
  )

# Step 3: Calculate MDC for each individual (for a 95% confidence level, Z = 1.96)
sd_by_individual <- sd_by_individual %>%
  mutate(
    MDC = 1.96 * SEM
  )

# View the final output with MDC for each individual and visit day
print(sd_by_individual)

# ADD TO PLOT...
# Assuming df_avg is your data frame and df contains the calculated MDC values per individual

# Merge the MDC data with the df_avg data (on ID and VisitDay)
plot_data <- df_avg %>% 
  filter(Time %in% c('PM')) %>%
  select(c('ID', 'Onset_Cx', 'VisitDay', 'Value_MSO', 'ISI_ms')) %>%
  filter(ISI_ms %in% c(2.5)) %>%
  group_by(ISI_ms, ID, VisitDay, Onset_Cx) %>%
  summarise(Ave_RMT_Change = mean(Value_MSO),
            Ave_SD = sd(Value_MSO, na.rm = TRUE)) %>%
  ungroup()

# Merging MDC calculated earlier into plot data
plot_data <- plot_data %>%
  left_join(sd_by_individual %>% select(ID, VisitDay, MDC), by = c("ID", "VisitDay"))

# Create the plot
plot <- plot_data %>%
  ggplot(aes(x = VisitDay, y = Ave_RMT_Change, 
             ymin = Ave_RMT_Change - Ave_SD, ymax = Ave_RMT_Change + Ave_SD, 
             group = Onset_Cx, color = Onset_Cx)) +
  geom_line(aes(y = Ave_RMT_Change, group = Onset_Cx, color = Onset_Cx)) +
  geom_point() +
  # annotate("text", 
  #          x = 2.5, y = max(plot_data$Ave_RMT_Change) + 5,  # Positioning text above legend
  #          label = "Characteristics\n201 --> L onset, LL\n202 --> NA R onset, Bulbar\n203 --> R onset, UL\n204 --> L onset, UL\n205 --> L onset, UL", 
  #          hjust = 0, vjust = 1, 
  #          size = 5, color = "black") +
  xlab("Day") + ylab("Inhibition (%)") +
  scale_y_continuous(breaks = seq(80, 140, by = 10)) +
  facet_wrap(~ ID) +
  theme_grey() +
  theme(axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        strip.text = element_text(size = 14),
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_errorbar(width = 0.2) +
  # Add error bars representing the MDC
  geom_errorbar(aes(ymin = Ave_RMT_Change - MDC, ymax = Ave_RMT_Change + MDC), width = 0.3, color = "red", linetype = "dashed")

# Print the plot
print(plot)

# ----------------------------------------
# PLOT of SICI - ave of ISIs
# .............Use the PMs for TXs...
# ----------------------------------------


plot_data <- df1 %>% 
  filter(Time %in% c('PM')) %>% # Onset_Cx_side
  select(c('ID','L_or_R_cx', 'VisitDay', 'Value_MSO', 'ISI_ms')) %>%    # Onset_Cx  
  filter(ISI_ms %in% c(2.5, 3)) %>%
  # filter(Visit_day %in% c('0_avg', '1_tx_day1','1_tx_day3','1_tx_day5','2_out_avg','3_fu_avg')) %>% # Onset_Cx_side
  group_by(ID, VisitDay, L_or_R_cx) %>% #Onset_Cx
  summarise(Ave_Diff = mean(Value_MSO),
            Ave_SD = sd(Value_MSO, na.rm = TRUE)) 


# # doing above to df1 now...
# 
# df$VisitDay <- as.character(df$VisitDay)  # Convert factor to character
# 
# # Remove "LCX ", "RCX ", "AM", and "PM"
# df$VisitDay <- gsub("LCX |RCX |AM|PM", "", df$VisitDay)
# 
# # Convert back to factor (if needed)
# df$VisitDay <- as.factor(df$VisitDay)
# 
# # Check unique values to confirm changes
# unique(df$VisitDay)


# plot plot_data <- L_or_R_cx
# NEED TO REDO for ONSET COrtex
plot1 <- df_avg %>% #plot_data %>% was df # was working df1
  filter(Time %in% c('PM')) %>% # Onset_Cx
  # filter(ISI_ms %in% c(2.5)) %>%
  select(c('ID','L_or_R_cx', 'VisitDay', 'Value_MSO', 'ISI_ms')) %>%    # Onset_Cx  
  # average over 2.5 and 3 or just 2.5
  filter(ISI_ms %in% c(3)) %>%
  group_by(ISI_ms, ID, VisitDay, L_or_R_cx) %>% #Onset_Cx
  summarise(Ave_RMT_Change = mean(Value_MSO),
            Ave_SD = sd(Value_MSO, na.rm = TRUE)
            ) %>%
  # summarise(Ave_Diff = ave(Diff_percent)) %>% 
  # mutate(name = fct_relevel(Visit_day, 
  #           "north", "north-east", "east", 
  #           "south-east", "south", "south-west", 
  #           "west", "north-west")) 
  ggplot(aes(x=VisitDay,y=Ave_RMT_Change, 
             ymin = Ave_RMT_Change-Ave_SD, ymax = Ave_RMT_Change+Ave_SD, 
             group_by = L_or_R_cx, color = L_or_R_cx)) +
  # add a line to mark the baseline
  geom_rect(aes(xmin = 0.3, xmax = 2.6, ymin = -Inf, ymax = Inf), 
            fill = "lightgrey", alpha = 0.06, color = NA) + 
  geom_line(aes(y = Ave_RMT_Change, group = L_or_R_cx, color = L_or_R_cx)) +
  geom_point() +
  annotate("text", x = 1.5, y = 140, label = "Baseline", size = 5) +  # Add text at (1.5, 140)
  xlab("Day") + ylab("Inhibition (%)") + #Change in Machine Intensity
  # scale_x_discrete(labels=c("B1", "B2","d1", "d5", "w3", "w5", "w7","w9", "w12","w16","w20","w24")) +
  # scale_y_continuous(breaks=seq(-20,40,by=10)) +
  scale_y_continuous(breaks=seq(80,120,by=10)) +
  facet_wrap( ~ ID) +
  theme_grey() + # theme_classic2
  theme(axis.title=element_text(size=14),
        axis.text=element_text(size=12),
        strip.text=element_text(size=14),
        axis.text.x = element_text(angle = 45, hjust = 1))

plot1 <- plot1 + geom_errorbar(width = 0.2)


# STYLE OPTIONS
# plot + theme(legend.position = c(0.9, 0.3))
# 
# plot + geom_rect(aes(xmin = 2, xmax = 3, ymin = -Inf, ymax = Inf), 
#             fill = "lightgrey", alpha = 0.2) +  # Highlight area between x = 2 and x = 3
#   theme_minimal()


# Create the OUTPUT directory if it doesn't exist
if (!dir.exists("4.Output")) {
  dir.create("4.Output")
}


# Save as PDF (Portrait)
ggsave("4.Output/Q2_tSICI_3.pdf", plot = plot1, width = 11, height = 8.5, units = "in")

# Save as PNG
ggsave("4.Output/Q2_tSICI_3.png", plot = plot1, width = 10, height = 8, dpi = 300)

# 201 --> L onset, LL
# 202 --> NA R onset, Bulbar
# 203 --> R onset, UL
# 204 --> L onset, UL
# 205 --> L onset, UL

# need to add SEMs for individual SICI Data!!

#### -------------------------------
# SICI Plot 2
#      with average over 2.5 and 3 ISI
#      PM only
#------------------------------------------------


plot2 <- df %>% #plot_data %>% 
  filter(Time %in% c('PM')) %>% # Onset_Cx
  select(c('ID','L_or_R_cx', 'VisitDay', 'Value_MSO', 'ISI_ms')) %>%    # Onset_Cx  
  # average over 2.5 and 3 or just 2.5
  filter(ISI_ms %in% c(2.5, 3)) %>%
  group_by(ID, VisitDay, L_or_R_cx) %>% #Onset_Cx
  summarise(Ave_RMT_Change = mean(Value_MSO),
            Ave_SD = sd(Value_MSO, na.rm = TRUE)) %>%
  ggplot(aes(x=VisitDay,y=Ave_RMT_Change, ymin = Ave_RMT_Change-Ave_SD, ymax = Ave_RMT_Change+Ave_SD, group_by = L_or_R_cx, color = L_or_R_cx)) +
  # add a horozontal loine for 100
  # geom_hline(yintercept = 100, linetype = "dashed", color = "black") +  # Add dashed line at y = 100
  # add a line to mark the baseline
  geom_rect(aes(xmin = 0.3, xmax = 2.6, ymin = -Inf, ymax = Inf), 
            fill = "lightgrey", alpha = 0.03, color = NA) + 
  geom_line(aes(y = Ave_RMT_Change, group = L_or_R_cx, color = L_or_R_cx)) +
  geom_point() +
  annotate("text", x = 1.5, y = 140, label = "Baseline", size = 5) +  # Add text at (1.5, 140)
  xlab("Day") + ylab("Inhibition (%)") + #Change in Machine Intensity
  # scale_x_discrete(labels=c("B1", "B2","d1", "d5", "w3", "w5", "w7","w9", "w12","w16","w20","w24")) +
  # scale_y_continuous(breaks=seq(-20,40,by=10)) +
  scale_y_continuous(breaks=seq(80,120,by=10)) +
  facet_wrap( ~ ID) +
  theme_grey() + # theme_classic2
  theme(axis.title=element_text(size=14),
        axis.text=element_text(size=12),
        strip.text=element_text(size=14),
        axis.text.x = element_text(angle = 45, hjust = 1))

plot2 <- plot2 + geom_errorbar(width = 0.2)


# Save as PDF (Portrait)
ggsave("4.Output/Q2_tSICI_no_line.pdf", plot = plot2, width = 11, height = 8.5, units = "in")


# Save as PNG
ggsave("4.Output/Q2_tSICI_no_line.png", plot = plot2, width = 10, height = 8, dpi = 300)

#### -------------------------------
# SICI Plot 3
#      with average over 2.5 and 3 ISI
#      and including AM and PM
#------------------------------------------------


# plot plot_data <- L_or_R_cx
plot3 <- df %>% #plot_data %>% 
  # filter(Time %in% c('PM')) %>% # Onset_Cx_side
  # filter(ISI_ms %in% c(2.5)) %>%
  select(c('ID','L_or_R_cx', 'VisitDay', 'Value_MSO', 'ISI_ms', 'Time')) %>%    # Onset_Cx  
  filter(ISI_ms %in% c(2.5, 3)) %>%
  group_by(ID, VisitDay, L_or_R_cx, Time) %>% #Onset_Cx # remove ISI and Time to average across it
  summarise(Ave_RMT_Change = mean(Value_MSO),
            Ave_SD = sd(Value_MSO, na.rm = TRUE)
            ) %>%
  ggplot(aes(x=VisitDay,y=Ave_RMT_Change, ymin = Ave_RMT_Change-Ave_SD, ymax = Ave_RMT_Change+Ave_SD, 
             group = interaction(L_or_R_cx, Time),  # Ensure Time is in the group, 
             color = L_or_R_cx, 
             shape = Time, 
             linetype = Time)) +
  # add a line to mark the baseline 
  geom_rect(aes(xmin = 2.3, xmax = 2.7, ymin = -Inf, ymax = Inf), 
            fill = "lightgrey", alpha = 0.05, color = NA) + 
  geom_line(size = 1) +  # Line size for visibility
  geom_point(size = 2) +  # Make points more visible
  xlab("Day") + 
  ylab("Inhibition (%)") + #Change in Machine Intensity
  scale_linetype_manual(values = c("AM" = "solid", "PM" = "dotted")) +  # AM solid, PM dotted
  scale_shape_manual(values = c("AM" = 16, "PM" = 17)) +  # AM = solid circle, PM = triangle
  scale_y_continuous(breaks=seq(80,120,by=10)) +
  facet_wrap( ~ ID) +
  theme_grey() + # theme_classic2
  theme(axis.title=element_text(size=14),
        axis.text=element_text(size=12),
        strip.text=element_text(size=14),
        axis.text.x = element_text(angle = 45, hjust = 1))

plot3 <- plot3 + geom_errorbar(width = 0.2)

# Save as PDF (Portrait)
ggsave("4.Output/Q2_tSICI_AM_PM.pdf", plot = plot3, width = 11, height = 8.5, units = "in")

# Save as PNG
ggsave("4.Output/Q2_tSICI_AM_PM.png", plot = plot3, width = 10, height = 8, dpi = 300)

                    


#### -------------------------------
# SICI Plot 4 - Individual ISI - selected by baseline highest SICI???
#      with interaction 2.5 and 3 ISI
#      PM only
#------------------------------------------------


# plot plot_data <- L_or_R_cx
plot4 <- df %>% #plot_data %>% 
  filter(Time %in% c('PM')) %>% # Onset_Cx_side
  # filter(ISI_ms %in% c(2.5)) %>%
  select(c('ID','L_or_R_cx', 'VisitDay', 'Value_MSO', 'ISI_ms')) %>%    # Onset_Cx  
  filter(ISI_ms %in% c(2.5, 3)) %>%
  mutate(ISI_ms = as.factor(ISI_ms)) %>%
  group_by(ID, VisitDay, L_or_R_cx, ISI_ms) %>% #Onset_Cx # remove ISI and Time to average across it
  summarise(Ave_RMT_Change = mean(Value_MSO),
            Ave_SD = sd(Value_MSO, na.rm = TRUE)
            ) %>%
  ggplot(aes(x=VisitDay,y=Ave_RMT_Change, ymin = Ave_RMT_Change-Ave_SD, ymax = Ave_RMT_Change+Ave_SD, 
             group = interaction(L_or_R_cx, ISI_ms),  # Ensure Time is in the group, 
             color = L_or_R_cx, 
             shape = ISI_ms, 
             linetype = ISI_ms)) +
  # add a line to mark the baseline 
  geom_rect(aes(xmin = 2.3, xmax = 2.7, ymin = -Inf, ymax = Inf), 
            fill = "lightgrey", alpha = 0.06, color = NA) + 
  geom_line(size = 1) +  # Line size for visibility
  geom_point(size = 2) +  # Make points more visible
  xlab("Day") + 
  ylab("Inhibition (%)") + #Change in Machine Intensity
  scale_linetype_manual(values = c("2.5" = "solid", "3" = "dotted")) +  # AM solid, PM dotted
  scale_shape_manual(values = c("2.5" = 16, "3" = 17)) +  # AM = solid circle, PM = triangle
  scale_y_continuous(breaks=seq(80,120,by=10)) +
  facet_wrap( ~ ID) +
  theme_grey() + # theme_classic2
  theme(axis.title=element_text(size=14),
        axis.text=element_text(size=12),
        strip.text=element_text(size=14),
        axis.text.x = element_text(angle = 45, hjust = 1))

plot4 <- plot4 + geom_errorbar(width = 0.2)

# Save as PDF (Portrait)
ggsave("4.Output/Q2_tSICI_by_ISI.pdf", plot = plot4, width = 11, height = 8.5, units = "in")

# Save as PNG
ggsave("4.Output/Q2_tSICI_by_ISI.png", plot = plot4, width = 10, height = 8, dpi = 300)

     
# BELOW NOT TESTED YET....

## ------------------------------------
#
# Joining plots in a pdf
#
## ------------------------------------

# Open PDF file
pdf("4.Output/Q2_TMS_SICI_combined_plots.pdf", width = 8, height = 10)

# Print each plot on a new page
print(plot1)  # Page 1
print(plot2)  # Page 2
print(plot3)  # Page 3

# Close the PDF file
dev.off()

## ------------------------------------
#
# Joining plots in a pdf
#
## ------------------------------------

library(ggplot2)
library(gridExtra)

# Open a PDF file to save plots
pdf("OUTPUT/combined_plots.pdf", width = 8, height = 10)

# Print each plot to the PDF
grid.arrange(plot1, plot2, plot3, ncol = 1)  # Arranges plots vertically

# Close the PDF device
dev.off()

## ------------------------------------
#
# Joining plots in a pdf
#
## ------------------------------------


library(patchwork)

# Combine plots
combined_plot <- plot1 / plot2 / plot3  # Stack plots vertically

# Save as PDF
ggsave("OUTPUT/combined_plots.pdf", plot = combined_plot, width = 8, height = 10)

```
## SICI plot - interim analysis
Notes:
201 - TX D5 - missing value for tSICI 2.5. Not in excel...
Nans in Data, remove


```{r plot_SICI_Q2, echo=FALSE}

# Make new data for average of baselines!!!

# go back and ermove LX and RX from Visit Day variable
# 
# df2 <- df %>% 
#   select(c('ID','L_or_R_cx', 'VisitDay', 'Time', 'Value_MSO', 'ISI_ms')) %>%      
#   filter(ISI_ms %in% c(2.5, 3)) %>%
#   filter(Time %in% c('PM')) %>% # Onset_Cx_side
#   filter(!VisitDay %in% c('BSL D2 PM','BSL D2 PM')) %>%
#   group_by(ID, VisitDay, L_or_R_cx) %>% #Onset_Cx_side
#   summarise(Ave_Diff = ave(Value_MSO),
#             Ave_SD = sd(Value_MSO, na.rm = TRUE)) %>%
#   # Ungroup to return to a normal data frame
#   ungroup()

# New attempt -- #Onset_Cx

Value_MSO

plot_data <- df %>%
  filter(Time %in% c("PM")) %>%
  select(c('ID','L_or_R_cx', 'VisitDay', 'Value_MSO', 'ISI_ms')) %>%       #Onset_Cx
  filter(ISI_ms %in% c(2.5)) %>%
  # filter(!VisitDay %in% c('001_BSL D1 PM','001_BSL D2 PM')) %>%
  group_by(ID, L_or_R_cx, VisitDay) %>% #Onset_Cx
  dplyr::summarize(Ave_MSO = mean(Value_MSO, na.rm = TRUE), sd_MSO = sd(Value_MSO, na.rm = TRUE)) 


  # # filter(VisitDay %in% c("00_1_BSL DAY1 AM", "00_2_BSL DAY2 AM", "00_1_BSL DAY1 PM", "00_2_BSL DAY2 PM")) %>%
  # summarise(Ave_Diff = ave(Value_MSO),
  #           Ave_SD = sd(Value_MSO, na.rm = TRUE)) %>%
  # # Ungroup to return to a normal data frame
  # ungroup()


  # mutate(
  #   VisitDay = case_when(
  #     all(c("00_1_BSL_DAY1_AM", "00_2_BSL DAY2 AM") %in% VisitDay) ~ "00_BSL_AM_AVE",
  #     all(c("00_1_BSL_DAY1_PM", "00_2_BSL DAY2 PM") %in% VisitDay) ~ "00_BSL_PM_AVE",
  #     TRUE ~ VisitDay
  #   )
  # ) %>%
  # # Group by the ID and VisitDay to calculate the average of TotalPulses
  # group_by(ID, VisitDay) %>%
  # mutate(Value_MSO = if_else(
  #   VisitDay %in% c("00_BSL_AM_AVE", "00_BSL_PM_AVE"),
  #   mean(Value_MSO, na.rm = TRUE),
  #   Value_MSO
  # )) %>%
  # # Ungroup to return to a normal data frame
  # ungroup()

  
# head(df2)

  # filter(Visit_day %in% c('0_avg', '1_tx_day1','1_tx_day3','1_tx_day5','2_out_avg','3_fu_avg')) %>% #
    
# plot

plot2 <- plot_data %>% 
  group_by(ID, VisitDay, Onset_Cx) %>% #Onset_Cx
  # summarise(Ave_Diff = ave(Diff_percent)) %>% 
  # mutate(name = fct_relevel(Visit_day, 
  #           "north", "north-east", "east", 
  #           "south-east", "south", "south-west", 
  #           "west", "north-west")) 
  ggplot(aes(x=VisitDay,y=Ave_MSO, ymin = Ave_MSO-sd_MSO, ymax = Ave_MSO+sd_MSO, group_by = Onset_Cx, colour = Onset_Cx)) +
  geom_line(aes(y = Ave_MSO, group = Onset_Cx, color = Onset_Cx)) +
  geom_point(aes(y = Ave_MSO, group = Onset_Cx, color = Onset_Cx)) +
  xlab("Day") + ylab("Inhibition (%MSO)") + #Change in Machine Intensity
  scale_x_discrete(labels=c("B_1","B_2","D1", "'D5","W3","W7","W9","W12","W16","W20","W24")) +
  scale_y_continuous(breaks=seq(-20,30,by=5)) +
  facet_wrap( ~ ID) +
  theme_grey() + #theme_classic theme_grey
  theme(axis.title=element_text(size=14),
        axis.text=element_text(size=12),
        strip.text=element_text(size=14))

plot2 + geom_errorbar(width = 0.2)
# 
# plot_data %>% distinct(VisitDay)
    
```

## SICI Plot - SAS style 

```{r plot_SICI_LP, echo=FALSE}

df2 <- df1 %>% 
  filter(Test %in% c('tSICIp')) %>% # Onset_Cx_side
  select(c('ID','L_or_R_cx', 'Visit_day', 'Diff_percent', 'ISI_ms')) %>%      
  filter(ISI_ms %in% c(2.5, 3)) %>%
  filter(Visit_day %in% c('0_avg','2_out_avg','3_fu_avg')) %>% # Onset_Cx_side # make these inline!!
  group_by(ID, Visit_day, L_or_R_cx) %>% #Onset_Cx_side
  summarise(Ave_Diff = ave(Diff_percent),
            Ave_SD = sd(Diff_percent, na.rm = TRUE)) 

# plot

plot2 <- df2 %>% 
  group_by(ID, Visit_day, L_or_R_cx) %>% #Onset_Cx_side
  # summarise(Ave_Diff = ave(Diff_percent)) %>% 
  # mutate(name = fct_relevel(Visit_day, 
  #           "north", "north-east", "east", 
  #           "south-east", "south", "south-west", 
  #           "west", "north-west")) 
  ggplot(aes(x=Visit_day,y=Ave_Diff, ymin = Ave_Diff-Ave_SD, ymax = Ave_Diff+Ave_SD, group_by = L_or_R_cx, colour = L_or_R_cx)) +
  geom_line(aes(y = Ave_Diff, group = L_or_R_cx, color = L_or_R_cx)) +
  geom_point(aes(y = Ave_Diff, group = L_or_R_cx, color = L_or_R_cx)) +
  xlab("Day") + ylab("Inhibition (%)") + #Change in Machine Intensity
  scale_x_discrete(labels=c("B","d8","d22")) +
  scale_y_continuous(breaks=seq(-20,30,by=5)) +
  facet_wrap( ~ ID) +
  theme_grey() + #theme_classic theme_grey
  theme(axis.title=element_text(size=14),
        axis.text=element_text(size=12),
        strip.text=element_text(size=14))

plot2 + geom_errorbar(width = 0.2)

    
```


### Check to see if plot matches Liane's 


```{r indiv_plots_SICI, echo=TRUE}

plot_data <- df1 %>% 
  filter(Test %in% c('tSICIp')) %>% # Onset_Cx_side
  select(c('ID','L_or_R_cx', 'VisitDay', 'Value_MSO', 'ISI_ms')) %>%      
  filter(VisitDay %in% c('BSL D1 PM')) %>% # Onset_Cx_side
  group_by(ID, L_or_R_cx, ISI_ms) %>% #Onset_Cx_side
  summarise(Ave_Diff = mean(Value_MSO),
            Ave_SD = sd(Value_MSO, na.rm = TRUE)) 

# plot 
plot <- plot_data %>% 
  group_by(ID, ISI_ms, L_or_R_cx) %>% #Onset_Cx_side
  # summarise(Ave_Diff = ave(Diff_percent)) %>% 
  # mutate(name = fct_relevel(Visit_day, 
  #           "north", "north-east", "east", 
  #           "south-east", "south", "south-west", 
  #           "west", "north-west")) 
  ggplot(aes(x=ISI_ms,y=Ave_Diff, ymin = Ave_Diff-Ave_SD, ymax = Ave_Diff+Ave_SD, group_by = L_or_R_cx, colour = L_or_R_cx)) +
  geom_line(aes(y = Ave_Diff, group = L_or_R_cx, color = L_or_R_cx)) +
  geom_point() +
  xlab("ISI") + ylab("Inhibition (%)") + #Change in Machine Intensity
  scale_y_continuous(breaks=seq(-20,100,by=20)) +
  facet_wrap( ~ ID) +
  theme_grey() + # theme_classic2
  theme(axis.title=element_text(size=14),
        axis.text=element_text(size=12),
        strip.text=element_text(size=14))
        
# plot + geom_errorbar(width = 0.2)
plot

    
```

### Questions for Liane:

Which days correspond to day  8 and day 22?

What is the average measures in timeline?

Why am I not getting both sides??

Which subject numbers correspond to which?


# SICI Stats - TBC

# SICF Plot - TBC

# SICF Stats - TBC

# RMT - TBC
